Non-word repetition in Yélî Dnye

### 2021-10-25 manuscript.Rmd
cleaning

There are some reasons to believe that Yélî Dnye put that hypothesis to a critical test: The phoneme inventory is both large and acoustically packed, in addition to containing several typologically infrequent (or unique) contrasts. One could then predict that correlations with typological frequency should be relatively weak because the ambient language puts more pressure on Yélî children to distinguish (perceptually and articulatorily) fine-grained phonetic differences than what is required of child speakers of other languages. On the other hand, it is also possible that this pressure gives Yélî children no benefit, and that some of these categories are simply acquired later in development. We can draw a parallel with children learning another Papuan language, Ku Waru, which has a packed inventory of lateral consonants; children do not make adult-like realizations of the more complex of these laterals (the pre-stopped velar lateral /ɡ͡ʟ/) till age 5 or 6 [@rumsey2017dependency]

>>>>

There are some reasons to believe that Yélî Dnye put that hypothesis to a critical test: The phoneme inventory is both large and acoustically packed, in addition to containing several typologically infrequent (or unique) contrasts. One could then predict that correlations with typological frequency should be relatively weak because the ambient language puts more pressure on Yélî children to distinguish (perceptually and articulatorily) fine-grained phonetic differences than what is required of child speakers of other languages. On the other hand, it is also possible that this pressure gives Yélî children no benefit, and that some of these categories are simply acquired later in development. We can draw a parallel with children learning another Papuan language, Ku Waru, which has a packed inventory of lateral consonants; children do not produce adult-like realizations of the more complex of these laterals (the pre-stopped velar lateral /ɡ͡ʟ/) until  5 or 6 years of age [@rumsey2017dependency]
